---
title: ""
author: "Daihao Wu, Benjamin He, Seehe Kim, Fred Peng, Tom Xu"
date: ""
output: pdf_document
---

```{r, echo = FALSE, message = FALSE}
# This line only installs lme4 if you haven't got it installed already
if(!("lme4" %in% installed.packages())) install.packages("lme4")

#install.packages("lme4")

library(tidyverse)
library(dplyr)
library(readr)
library(readxl)
library(janitor)
library(ggplot2)
library(gridExtra)
library(lme4)
library(lmerTest)
library(VIM)
# Will's EDA in Passive air - PUF sheet
# House ID has already been changed to House_ID and Sample ID has already been changed to Sample_ID; A null values had been refilled;
```

```{r, echo = FALSE}
concentration_data = read_excel("NHS_2023_Data_October_31_University of Toronto_First phase_modified_Will.xlsx", sheet = "Passive air- PUF(pgm-3)", skip = 4)
selected_concentration_data <- concentration_data[, 1:15]

tech_survey_data = read_excel("20231027_Technician Survey Data.xlsx")
tech_survey_data <- tech_survey_data %>% 
  select(id, base_ac_yn, hrv_on_yn)
survey_data <- read_excel("20231027_0-12 Month Questionnaire Data.xlsx") %>% select(id, low_VOC_home, paints_yn)
selected_survey_data <- survey_data[1:44,]

merged_data = merge(selected_concentration_data, tech_survey_data, by.x = 'House_ID', by.y='id')
full_data1 = merge(merged_data, selected_survey_data, by.x = 'House_ID', by.y='id')
full_data <- full_data1 %>% 
  mutate(low_VOC_home = ifelse(is.na(low_VOC_home), 0, low_VOC_home)) %>% mutate(paints_yn = ifelse(is.na(paints_yn), 0, paints_yn))


# filter to only for the houses

# Change the period from text to numerical data
full_data = full_data %>% mutate(Period = case_when(Period == "0 month" ~ 0, Period == "3 month" ~ 3, Period == "6 month" ~ 6, Period == "9 month" ~ 9)) 

full_data = full_data %>% mutate(House_ID = case_when(House_ID == "NHAQS-001" ~ 1, House_ID == "NHAQS-002" ~ 2,House_ID == "NHAQS-003" ~ 3,House_ID == "NHAQS-004" ~ 4,House_ID == "NHAQS-005" ~ 5,House_ID == "NHAQS-006" ~ 6,House_ID == "NHAQS-007" ~ 7,House_ID == "NHAQS-008" ~ 8,House_ID == "NHAQS-009" ~ 9,House_ID == "NHAQS-010" ~ 10,House_ID == "NHAQS-011" ~ 11,House_ID == "NHAQS-012" ~ 12,House_ID == "NHAQS-013" ~ 13,House_ID == "NHAQS-014" ~ 14,House_ID == "NHAQS-015" ~ 15,House_ID == "NHAQS-016" ~ 16,))
  
#head(full_data)

#Convert all number strings to numeric
full_data$DEP <- as.numeric(full_data$DEP)
full_data$DPP <- as.numeric(full_data$DPP)
full_data$DiBP <- as.numeric(full_data$DiBP)
full_data$DnBP <- as.numeric(full_data$DnBP)
full_data$BzBP <- as.numeric(full_data$BzBP)
full_data$DEHP <- as.numeric(full_data$DEHP)
full_data$DnOP <- as.numeric(full_data$DnOP)
full_data$DiNP <- as.numeric(full_data$DiNP)
```



FCS_LMM_LN-het Method Starts:

```{r}

#Data preparation
full_data <- full_data %>% complete(nesting(House_ID), Period = seq(min(Period), max(Period),3), explicit = FALSE) %>% group_by(House_ID) %>% select(House_ID, Period, 'Start date (yyyy-mm-dd)', DEP, DPP, DiBP, DnBP, BzBP, DEHP, DnOP, DiNP, paints_yn, low_VOC_home, hrv_on_yn, base_ac_yn)

colnames(full_data)[colnames(full_data) == 'Start date (yyyy-mm-dd)'] <- "StartDate"

full_data$StartDate <- substr(full_data$StartDate, 1, 7)

dep_data <- full_data %>% 
  select(House_ID, Period, DEP, low_VOC_home)

dpp_data <- full_data %>% 
  select(House_ID, Period, DPP, low_VOC_home)

dibp_data <- full_data %>% 
  select(House_ID, Period, DiBP, low_VOC_home)

dnbp_data <- full_data %>% 
  select(House_ID, Period, DnBP, low_VOC_home)

bzbp_data <- full_data %>% 
  select(House_ID, Period, BzBP, low_VOC_home)

dehp_data <- full_data %>% 
  select(House_ID, Period, DEHP, low_VOC_home)

dnop_data <- full_data %>% 
  select(House_ID, Period, DnOP, low_VOC_home)

dinp_data <- full_data %>% 
  select(House_ID, Period, DiNP, low_VOC_home)

```

```{r}
# #write.csv(dpp_data, "dpp_data.csv", row.names=FALSE)
# 
# library(car)
# 
# # Assuming dpp_data is your dataset and DPP is the dependent variable
# # Fit a linear model using all other variables as predictors
# # Note: Replace `predictor1`, `predictor2`, ..., with your actual predictor variable names
# model <- lmer(DPP ~ Period + (1|House_ID), data=dpp_data)
# summary(model)
# # Calculate VIF
# #vif_values <- vif(model)
# 
# # Print VIF values
# #print(vif_values)
# 
# # Identify variables with high VIF
# #high_vif <- vif_values[vif_values > 5]  # Adjust the threshold as necessary
# #print(high_vif)
```

Notice from above result, we notice that singular fit problem occurred, so we could not impute all the variables at once, because it the complexity of the model would not produce effective results.
```{r}
library(mice)
library(micemd)
library(miceadds)
library(nlme)
library(geepack)
set.seed(1)
# Setup for imputation for only DPP

vars <- colnames(dpp_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["DPP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["DPP"] <- "2l.continuous"

imputed_data <- complete(mice(data=dpp_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert DPP to character to accommodate both numeric values and "DL"
imputed_data$DPP <- as.character(imputed_data$DPP)

# Replace values below 19 with "DL"
imputed_data$DPP[imputed_data$DPP < 19] <- "DL"

# Filter out rows where DPP is "DL"
imputed_data <- imputed_data %>% filter(DPP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(DPP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 3

```{r}

confint(model_imp_3)
summary(model_imp_3)

```

Similarly, we would do it for dep:

```{r}
set.seed(1)
# Setup for imputation for only DPP

vars <- colnames(dep_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["DEP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["DEP"] <- "2l.continuous"

imputed_data <- complete(mice(data=dep_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert DEP to character to accommodate both numeric values and "DL"
imputed_data$DEP <- as.character(imputed_data$DEP)

# Replace values below 99 with "DL"
imputed_data$DEP[as.numeric(imputed_data$DEP) < 99] <- "DL"

# Filter out rows where DEP is "DL"
imputed_data <- imputed_data %>% filter(DEP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(DEP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 2

```{r}

confint(model_imp_2)
summary(model_imp_2)

```

Similarly, we would do it for dehp:

```{r}
set.seed(1)
# Setup for imputation for only dehp

vars <- colnames(dehp_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["DEHP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["DEHP"] <- "2l.continuous"

imputed_data <- complete(mice(data=dehp_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert DEHP to character to accommodate both numeric values and "DL"
imputed_data$DEHP <- as.character(imputed_data$DEHP)

# Replace values below 231 with "DL"
imputed_data$DEHP[imputed_data$DEHP < 231] <- "DL"

# Filter out rows where DEHP is "DL"
imputed_data <- imputed_data %>% filter(DEHP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(DEHP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 3

```{r}

confint(model_imp_3)
summary(model_imp_3)

```











Similarly, we would do it for dihp:

```{r}
set.seed(1)
# Setup for imputation for only dehp

vars <- colnames(dinp_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["DiNP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["DiNP"] <- "2l.continuous"

imputed_data <- complete(mice(data=dinp_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert DiNP to character to accommodate both numeric values and "DL"
imputed_data$DiNP <- as.character(imputed_data$DiNP)

# Replace values below 168 with "DL"
imputed_data$DiNP[imputed_data$DiNP < 168] <- "DL"

# Filter out rows where DiNP is "DL"
imputed_data <- imputed_data %>% filter(DiNP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(DiNP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 1

```{r}

confint(model_imp_1)
summary(model_imp_1)

```








Similarly, we would do it for dibp:

```{r}
set.seed(1)
# Setup for imputation for only dehp

vars <- colnames(dibp_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["DiBP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["DiBP"] <- "2l.continuous"

imputed_data <- complete(mice(data=dibp_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert DiBP to character to accommodate both numeric values and "DL"
imputed_data$DiBP <- as.character(imputed_data$DiBP)

# Replace values below 198 with "DL"
imputed_data$DiBP[imputed_data$DiBP < 198] <- "DL"

# Filter out rows where DiBP is "DL"
imputed_data <- imputed_data %>% filter(DiBP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(DiBP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 2

```{r}

confint(model_imp_2)
summary(model_imp_2)

```






Similarly, we would do it for dnbp:

```{r}
set.seed(1)
# Setup for imputation for only dnbp

vars <- colnames(dnbp_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["DnBP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["DnBP"] <- "2l.continuous"

imputed_data <- complete(mice(data=dnbp_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert DnBP to character to accommodate both numeric values and "DL"
imputed_data$DnBP <- as.character(imputed_data$DnBP)

# Replace values below 19 with "DL"
imputed_data$DnBP[imputed_data$DnBP < 19] <- "DL"

# Filter out rows where DnBP is "DL"
imputed_data <- imputed_data %>% filter(DnBP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(DnBP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 2

```{r}

confint(model_imp_2)
summary(model_imp_2)

```





Similarly, we would do it for bzbp:

```{r}
set.seed(1)
# Setup for imputation for only bzbp

vars <- colnames(bzbp_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["BzBP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["BzBP"] <- "2l.continuous"

imputed_data <- complete(mice(data=bzbp_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert BzBP to character to accommodate both numeric values and "DL"
imputed_data$BzBP <- as.character(imputed_data$BzBP)

# Replace values below 36 with "DL"
imputed_data$BzBP[imputed_data$BzBP < 36] <- "DL"

# Filter out rows where BzBP is "DL"
imputed_data <- imputed_data %>% filter(BzBP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(BzBP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 1

```{r}

confint(model_imp_1)
summary(model_imp_1)

```






Similarly, we would do it for dnop:

```{r}
set.seed(1)
# Setup for imputation for only dnop

vars <- colnames(dnop_data) # Assuming DPP concentration and related variables are columns
V <- length(vars) # Number of variables

# Initialize predictor matrix (adjust based on actual variables and their relationships)
predmat <- matrix(1, nrow = V, ncol = V)  # Start with all as potential predictors
diag(predmat) <- 0
rownames(predmat) <- vars
colnames(predmat) <- vars
predmat["DnOP", "House_ID"] <- -2

# Define imputation methods 
impmeth <- rep("pmm", V)
names(impmeth) <- vars
impmeth["DnOP"] <- "2l.continuous"

imputed_data <- complete(mice(data=dnop_data, method=impmeth, predictorMatrix=predmat, diagnostics=TRUE, maxit=5, m=5, remove.collinear=FALSE), action = "long", include = FALSE)

# Convert DnOP to character to accommodate both numeric values and "DL"
imputed_data$DnOP <- as.character(imputed_data$DnOP)

# Replace values below 48 with "DL"
imputed_data$DnOP[imputed_data$DnOP < 48] <- "DL"

# Filter out rows where DnOP is "DL"
imputed_data <- imputed_data %>% filter(DnOP != "DL")

write.csv(imputed_data, "output_data.csv", row.names = FALSE)
```



```{r}
library(data.table)
# Load the dataset
output_data <- fread("output_data.csv")

# Split the dataset by the .imp column
split_datasets <- split(output_data, output_data$.imp)

models <- list()

# Loop through each split dataset
for (imp_value in names(split_datasets)) {
  # Extract the current dataset
  current_dataset <- split_datasets[[imp_value]]
  
  # Fit the linear mixed model
  # Assuming 'Period' and other relevant independent variables are in your dataset
  # Adjust the formula as necessary to include the correct independent variables
  model <- lmer(log(as.numeric(DnOP)) ~ Period + (1|House_ID), data = current_dataset)
  
  # Store the model in the models list, naming it by the .imp value
  models[[imp_value]] <- model
}

# Accessing a specific model
# For example, to access the model for .imp = 1
model_imp_1 <- models[['1']]
model_imp_2 <- models[['2']]
model_imp_3 <- models[['3']]
model_imp_4 <- models[['4']]

# Summary of the model

# Get the residuals from the model
residuals_1 <- residuals(model_imp_1)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_1^2)
mse

residuals_2 <- residuals(model_imp_2)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_2^2)
mse

residuals_3 <- residuals(model_imp_3)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_3^2)
mse

residuals_4 <- residuals(model_imp_4)
# Calculate Mean Squared Error (MSE)
mse <- mean(residuals_4^2)
mse

```
from the above mse we select the one with smallest, so we use result from imp = 1

```{r}

confint(model_imp_1)
summary(model_imp_1)

```